Cluster Dynamics with HETDEX - I: Simulated Performance, Mass Distribution and Limits

### 2016-02-04 ms.tex
keep working

\newcommand{\editorial}[1]{\textcolor{red}{#1}}
\DeclareRobustCommand{\ion}[2]{%
\relax\ifmmode
\ifx\testbx\f@series
{\mathbf{#1\,\mathsc{#2}}}\else
{\mathrm{#1\,\mathsc{#2}}}\fi
\else\textup{#1\,{\mdseries\textsc{#2}}}%
\fi}
\newcommand{\multic}[2]{\multicolumn{#1}{c}{#2}}

@@

\editorial{Give outline of paper section.}

@@

\section{Data and Mock Observations}\label{sec: Data}

@@

\section{Recovery of Parameters}\label{sec: recovery}
 In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. This is not meant to be an exhaustive study of the different methods used to recover these parameters. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with observational studies.

@@

\section{RESULTS}\label{sec: results}
Here we explore the cluster member recovery rate and mass estimates for the two observing strategies. We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.

@@

Both of the figures shown below show the predicted versus true cluster masses for each of the two observing strategries. In each panel the solid black line is the 1:1 relationship, the solid colored line is the median recovered mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles). The lower panels show the fractional cluster mass error: 
\begin{equation}\label{eq: fractional error}
	\epsilon = (M_{pred} - M)/M
\end{equation}
where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.

@@

\subsubsection{Probability Based}
Figure \ref{fig:Probability comparison} shows the cluster mass predictions for the power law scaling relation and the probability based method with different input features.

@@

\subsubsection{Machine Learning Based}
Figure \ref{fig: ML comparison} show the power law predictions compared to the RF predictions using LOSVD ($\sigma$) combined with both $z$ and the number of galaxies observed, $N_{gal}$.  
\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass. The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The solid black line shows the 1:1 relation. The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions represent the 68\% scatter around the median values.} \label{fig: ML comparison} 
\end{figure*}

@@

\begin{table*}
\centering
\caption{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
	\begin{tabular}{ccccccc}
		%\hline
		& \multic{3}{Targeted} & \multic{3}{Survey} \\
		\cline{2-4} \cline{5-7}
		Input Features & MAE (dex) & RMSE (dex) & Overlap & MAE (dex) & RMSE (dex) & Overlap \\
		\hline \hline
		Power Law & 0.263 & 0.396 & --- & 0.263 & 0.393 & --- \\
		$\sigma$ & 0.246 & 0.361 & --- & 0.238 & 0.344 & --- \\
		$\sigma, z$ & 0.193 & 0.285 & --- & 0.171 & 0.260 & --- \\
		$\sigma, z, N_{gal}$ & 0.117 & 0.193 & --- & 0.093 & 0.179 & --- \\

		\hline
	\end{tabular}
\label{tbl: derived parameters}
\end{table*}

\section{HETDEX as a Galaxy Cluster Survey}

\subsection{Expected Results}
\editorial{This is where I am going to discuss the redMapper stuff.}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Potential Improvements}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Extendability to Other Surveys}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{SUMMARY}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\newcommand{\editorial}[1]{\textcolor{red}{#1}}
\DeclareRobustCommand{\ion}[2]{%
\relax\ifmmode
\ifx\testbx\f@series
{\mathbf{#1\,\mathsc{#2}}}\else
{\mathrm{#1\,\mathsc{#2}}}\fi
\else\textup{#1\,{\mdseries\textsc{#2}}}%
\fi}
\newcommand{\multic}[2]{\multicolumn{#1}{c}{#2}}
\newcommand{\rottext}[2]{\multirow{#1}{*}{\rotatebox[origin=c]{90}{#2}}}

@@

We begin in Section \ref{sec:Data} by giving an overview of what data is used, how it is created, and how we make our ``observations.'' Details about the determination of cluster parameters, velocity dispersion, total mass, etc., are discussed in Section \ref{sec:recovery}. Next, we present the results of our study in Section \ref{sec:results} and discuss their implications in Section \ref{sec:discussion}. Finally we summarize our findings in Section \ref{sec:summary}.

@@

\section{Data and Mock Observations}\label{sec:Data}

@@

\section{Recovery of Parameters}\label{sec:recovery}
 In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. This is not meant to be an exhaustive study of the different methods used to recover these parameters. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with observational studies.

@@

\section{RESULTS}\label{sec:results}
Here we explore the cluster member recovery rate and mass estimates for the two observing strategies. We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.

@@

@@

\begin{table*}
\centering
\caption{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
\begin{tabular}{cccccccc}
	%\hline
	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
	\cline{3-5} \cline{6-8}
	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
	\hline
	\rottext{4}{Prob Based} & Power Law & 0.263 & 0.396 & --- & 0.263 & 0.393 & --- \\
	&$\sigma$ & 0.220 & 0.335 & --- & 0.222 & 0.329 & --- \\
	&$\sigma, z$ & 0.189 & 0.286 & --- & 0.194 & 0.278 & --- \\
	&$\sigma, z, N_{gal}$ & 0.129 & 0.207 & --- & 0.140 & 0.222 & --- \\

	\hline
	\rottext{4}{ML Based} & Power Law & 0.263 & 0.396 & --- & 0.263 & 0.393 & --- \\
	&$\sigma$ & 0.246 & 0.361 & --- & 0.238 & 0.344 & --- \\
	&$\sigma, z$ & 0.193 & 0.285 & --- & 0.171 & 0.260 & --- \\
	&$\sigma, z, N_{gal}$ & 0.117 & 0.193 & --- & 0.093 & 0.179 & --- \\

	\hline
\end{tabular}
\label{tbl:mass comparisons}
\end{table*}

The MAE and RMSE associated with the ensemble of predictions are summarized in Table \ref{tbl:mass comparisons}. As expected, we find that both the probability based and ML based methods out perform the standard power law based methods for both the targeted and survey observations. We also find that the ML based method produces lower ensemble error for both the observation strategies when compared to the probability based method, although the MAE and RMSE are reduced by only $\sim0.01$ dex. \editorial{here is where we would talk about cross validation on the errors.}

In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted versus true cluster masses for each of the two observing strategries. In each panel the solid black line is the 1:1 relationship, the solid colored line is the median recovered mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles). The lower panels show the fractional cluster mass error: 
\begin{equation}\label{eq: fractional error}
	\epsilon = (M_{pred} - M)/M
\end{equation}
where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.

In both figures we successively add additional information to further contrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}). The power law derived masses, using the single (not including the cosmological parameters) free parameter, $\sigma$ (the LOSVD), over estimates the predicted cluster mass at all masses. Both the probability and ML methods over predict the mass of low mass clusters and under predict the mass of the higher mass clusters. When the redshift information is also added, the amount of this over and under prediction is lessened but the cross over point, remains roughly consistent at $\sim10^{14}$ \msol. Additionally, the number of galaxies observed, $N_{gal}$, further reduces the MAE and RMSE on the predictions but also lowers the cross over point to $\sim10^{13.5}$ \msol.

@@

\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass. The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The solid black line shows the 1:1 relation. The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions represent the 68\% scatter around the median values.} \label{fig: ML comparison} 
\end{figure*}

@@

\section{HETDEX as a Galaxy Cluster Survey}\label{sec:discussion}

\subsection{Expected Results}
\editorial{Expected results in what context? How well we can obtain cluster masses? How many masses will we get to what accuracy? This is sorta talk about in the results section but we don't really come out and say "this is what we think HETDEX will and and how well we think it will do it." That might worth saying, even if we are wrong it will give people a starting point when thinking about this stuff in the future.}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Potential Improvements}
\editorial{The potential improvements are really three fold. We know that the observing won't cover all of the sky. So we can simply tile more and try to get more clusters. We can observe deeper. I'm not sure the current exposure times (they are in an email that I sent to casey) but if we can extend them, then we can get further down the IMF and try to build up some of the clusters that are really more like groups than anything else. The last thing we can do is to attempt to  build better models to make better predictions on the masses. That might be something like the study that \cite{Acquaviva2016} did with the stellar metallicities. Or we'll need something else that I haven't thought of just yet.}

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Extendability to Other Surveys}
\editorial{This is where I am going to discuss the redMapper stuff. In this section I want to talk about the calibration of the red sequence (i think), and how we might be able to use HETDEX to help nail that down and then use those relationships to better calibrate the cluster masses coming out of DES and LSST. Other surveys that we can think of that people might apply this sort of method to? GOGREEN? GAMA? There are going to be a good number of blind photometric surveys, but I can't really think of another blind spectroscopy survey or some survey that is designed to one specific thing that we can try to co-opt to do what we want.}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{SUMMARY}\label{sec:summary}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

It is our hope that this work may be useful to others when conducting their own research. Because this work relies heavily on (often) complex data analysis, and in order to promote transparency, we provide all of the code used to conduct this study at https://github.com/boada/desCluster. Regrettably, large file size prevents including the source data with the analysis routines. The authors are happy to provide them, if requested.
